Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-06-06 paper/paper.tex
revise section 7

The second operator @choices@ is implemented with delimited control operator 
@shift@ but simply calls our first operator @nd@ in body.

@@

Now we can use these two operators to redefine @aeval@.
We add an annotation \verb|@cps[Ans]| on the return type of the @aeval@ function to enable
applying delimited control operators.
Then, for every nondeterministic choice in the abstract interpreter, we can simply call 
@choices@ on the set of possible choices and write the program sequentially as concrete 
interpreters, and the subsequent statements and expressions become the delimited continuation
@f@. @choices@ also returns the latest cache to its left-hand side definition.
The cache is still accumulated to the next call to @choices@ or @aeval@, 
given the fact that the abstract interpreter should always use the latest cache.

>>>>

The second operator @choices@ is implemented with delimited control operator 
@shift@ but simply calls our first operator @nd@ in its body.

@@

Now we can use these two operators to redefine @aeval@. The abstract evaluator @aeval@ is
rewritten in direct-style, so that the last argument @cont@ disappears; we also add an 
annotation \verb|@cps[Ans]| on the return type to enable using delimited control operators 
in it.
Then, for every nondeterministic choice in the abstract interpreter, we can simply call 
@choices@ on the set of possible choices and write the program sequentially as concrete 
interpreters, and the subsequent statements and expressions become the delimited continuation
@f@. @choices@ also returns the latest cache to its left-hand side definition.
The cache is still accumulated to the next call to @choices@ or @aeval@, 
given the fact that the abstract interpreter should always use the latest cache.
